---
title: "IDEEA model R-package development, step-by-step"
author: '@IDEEA'
date: "3/29/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

```{r}

```



The goal if this file is to document the process of creation of the IDEEA model package. Steps:  

*2023-08-01..+*

## Technologies with costs
```{r}
library(tidyverse)
f <- "data-raw/Data Generation_and_Storage_of_ElectricityExcel.xlsx"
sheets <- readxl::excel_sheets(f)

s <- sheets[2]
readxl::read_excel(f, s, "B4:F43") %>% rename(parameter = `...1`) %>%
  filter(!is.na(`2020`) | !is.na(`2030`) | !is.na(`2040`) | !is.na(`2050`)) %>%
  filter(!grepl("Gross Heat", parameter, ignore.case = T)) %>%
  filter(!grepl("Startup cost", parameter, ignore.case = T))
  as.data.table()

```

```{r}
# transmission_5x5 <- googlesheets4::read_sheet(
#   "https://docs.google.com/spreadsheets/d/1LF6aBkFF0o3tq-9l5OglL8A4eukG_en2pVQS7VKb23c/edit#gid=1904567822",
#   "transmission_5x5",
#   skip = 1
# )
# 
# transmission_5x5 <- transmission_5x5 %>%
#   pivot_longer(cols =  3:ncol(x), names_to = "dst", values_to = "MW") %>%
#   filter(!is.na(MW))
# 
# 
# save(transmission_5x5, file = "data-raw/googlesheets/transmission_5x5.RData")

```



*2023-07-17..21*
* WRI power plants data  
  + 

* write-up requests:
  describe coal (oil/gas/...) resources:   
  * 1-2 paragraphs with importance of coal for Indian economy   
  * locations of the main deposits and mines   
  * export and import of coal (which regions, mines, types of coal)  
  * historical prices (by region/source)  
  * elaboration on unexplored resources  
  * link to environmental impact (air, water, land)  
  [references]

## WRI - select India data  
```{r}
library(tidyverse)
library(sf)
(load("data-raw/wri.RData"))
gis_sf <- IDEEA.dev:::ideea_map %>%
  filter(!is.na(reg46)) %>% 
  mutate(
    region = reg46,
    reg_off = if_else(offshore, paste0(reg46, "_off"), reg46), 
    .before = 1)
# gis_sf <- get_ideea_map(nreg = 46, offshores = T, islands = T) %>% 
#   mutate(region = reg46, .before = 1)


gis_sf$offshore %>% summary()
gis_sf[is.na(gis_sf$offshore),]
gis_sf$reg_off
# gis_sf <- IDEEA.dev::get_ideea_map(34, offshores = T, islands = T)

w <- wri %>% filter(country == "IND")
# w$latitude %>% summary()
wri_sf <- st_as_sf(w, coords = c("longitude", "latitude")) %>%
  st_set_crs(st_crs(gis_sf))

x <- st_within(wri_sf, gis_sf, sparse = F)
# x <- st_intersects(wri_sf, gis_sf)
# x
class(x); dim(x)
x <- apply(x, 1, which.max)
summary(x)
length(x); dim(w)
summary(unlist(x)); dim(gis_sf)

wri_sf %>% class()
wri_sf <- wri_sf %>% 
  mutate(
    reg_off = gis_sf$reg_off[unlist(x)],
    .before = 1
  )

ii <- gis_sf$reg_off %in% unique(wri_sf$reg_off)
summary(ii); unique(gis_sf$reg_off[ii])
gis_sf[!ii, 1] %>% plot()
na <- wri_sf %>% filter(is.na(reg_off))

# plot(gis_sf[1], col = "grey", reset = F)
# plot(na[1], col = "red", add = T)
# st_nearest_feature(na, gis_sf)

gis_sf %>%
  left_join(
    st_drop_geometry(wri_sf),
    by = "reg_off"
  )

wri_sf <- wri_sf %>%
  left_join(
    st_drop_geometry(gis_sf),
    by = "reg_off"
  )
save(wri_sf, file = "data-raw/wri_sf.RData")

wri_sf$other_fuel1 %>% unique()
wri_sf$other_fuel2 %>% unique()
wri_sf$other_fuel3 %>% unique()

wri_reg46 <- wri_sf %>% 
  st_drop_geometry() %>%
  group_by(reg_off, primary_fuel, mainland, offshore,
           across(matches("reg"))) %>%
  summarise(
    commissioning_year = mean(as.numeric(commissioning_year), 
                              na.rm = T) %>% round(),
    year_of_capacity_data = mean(as.numeric(year_of_capacity_data), 
                                 na.rm = T) %>% round(),
    capacity_mw = sum(capacity_mw, na.rm = T),
    generation_gwh_2013 = sum(generation_gwh_2013, na.rm = T),
    generation_gwh_2014 = sum(generation_gwh_2014, na.rm = T),
    generation_gwh_2015 = sum(generation_gwh_2015, na.rm = T),
    generation_gwh_2016 = sum(generation_gwh_2016, na.rm = T),
    generation_gwh_2017 = sum(generation_gwh_2017, na.rm = T),
    generation_gwh_2018 = sum(generation_gwh_2018, na.rm = T),
    generation_gwh_2019 = sum(generation_gwh_2019, na.rm = T),
    generation_gwh_max = max(generation_gwh_2013, generation_gwh_2014,
                             generation_gwh_2015, generation_gwh_2016,
                             generation_gwh_2017, generation_gwh_2018,
                             generation_gwh_2019, na.rm = T),
    .groups = "drop"
  ) %>%
  as.data.table()
wri_reg46$primary_fuel %>% unique()

save(wri_reg46, file = "data-raw/wri_reg46.RData")

```

## Loadcurve
```{r}
reg_tbl <- IDEEA.dev::ideea_data$reg_tbl %>% 
  filter(!is.na(reg36), !offshore) %>% unique()

if (!file.exists("data-raw/load_2019.RData")) {
  x <- readxl::read_excel("data-raw/Dem_2019.xlsx", range = "B3:LXZ35")
  names(x) <- c("reg36", tsl_d365_h24$tsl_sets$slice)
  all(x$reg36 %in% reg_tbl$reg36) # check - all TRUE
  
  
  load_2019 <- x %>% 
    pivot_longer(cols = starts_with("d"), names_to = "slice", 
                 values_to = "MWh") %>%
    left_join(
      unique(
        select(reg_tbl, reg36, reg7)), by = "reg36"
      )
  save(load_2019, file = "data-raw/load_2019.RData")    
} else {
  (load("data-raw/load_2019.RData"))
}

# filter outliers
load_2019 <- load_2019 %>%
  mutate(
    datetime = timeslices::tsl2dtm(slice, tmz = "Asia/Kolkata", year = 2019),
    MONTH = timeslices::tsl2month(slice),
    YDAY = timeslices::tsl2yday(slice),
    HOUR = timeslices::tsl2hour(slice),
    .after = "slice"
  )

load_2019_summary <- load_2019 %>% 
  # ungroup() %>%
  group_by(reg36, reg7) %>%
  summarize(mean_MWh = mean(MWh), sd_MWh = sd(MWh), .groups = "drop")
load_2019_summary$mean_MWh %>% unique() %>% length()

n_sd <- 3
load_2019_clean <- load_2019 %>%
  left_join(load_2019_summary) %>%
  # rowwise() %>%
  mutate(
    # MWh_clean = ifelse(MWh > mean_MWh + n_sd * sd_MWh,
    #                     mean_MWh + n_sd * sd_MWh,
    #                     if_else(MWh < mean_MWh - n_sd * sd_MWh,
    #                             mean_MWh - n_sd * sd_MWh,
    #                             mean_MWh)
    #                     ),
    MWh_outlier = if_else(abs(MWh - mean_MWh) > n_sd * sd_MWh, TRUE, FALSE)
  ) %>% 
  mutate(
    MWh_clean = if_else(MWh_outlier, mean_MWh, MWh)
  ) %>%
  as.data.table()
# dx <- diff(c(load_2019_clean$MWh, load_2019_clean$MWh[1])) / load_2019_clean$sd_MWh
# summary()
load_2019_clean
load_2019_clean$MWh_outlier %>% summary()
  

ggplot(load_2019_clean) +
  geom_line(aes(HOUR, MWh_clean/1e3, color = YDAY, group = YDAY), alpha = .25) +
  scale_color_viridis_c(option = "H", limits = c(1, 365)) +
  geom_line(aes(HOUR, MWh_clean/1e3, color = YDAY, group = YDAY), alpha = .25) +
  facet_wrap(~reg36, ncol = 4, scales = "free_y") +
  labs(y = "GWh", x = "hour") +
  theme_bw()


load_2019_clean %>%
  mutate(MWh = MWh_clean) %>%
  select(
    any_of(c("reg36", "reg7", "datetime", "slice", "MWh"))
  )
save(load_2019_clean, file = "data-raw/load_2019_clean.RData")
```


## Time slices (internal)
```{r}
tsl_d365_h24 <- list(
  tsl_levels = list(ANNUAL = "ANNUAL", timeslices::tsl_levels$d365_h24),
  tsl_sets = mutate(
    timeslices::tsl_sets$d365_h24,
    slice = paste(YDAY, HOUR, sep = "_")
  )
)
save(tsl_d365_h24, file = "data-raw/tsl_d365_h24.RData")
tsl_d365_h24$tsl_sets
tsl_d365_h24$tsl_levels

```


*2023-07-10..12:*  
* rebuilding maps-objects
  + dropping `sp` format (since it is based on the )
  + using GWA offshore areas, split/assign the areas using Voronoi algo..
  + keep regional splits: 36, 34, (32?), 7, 5 regions and 1 (national)
  + all maps have offshore area
  + ROW is a separate map in ... CRS/projection
* add regions-mapping table (start from 46, 36, ...)
* connect inputs from Google-Sheets, imported:
  + Wind
  + Solar
  + Gas
  + Coal
  + Lignite
  missing:
  - CCS
  - 
* add transmission table for every map/aggregation
  + 5 & 7 r
  - 36
  - 34
  - 32
* capacity from WRI
* added correlation-based clusters for wind and solar
  + 36 region w/offshore
* adding dependencies (see below and `desc`)

## redoing all maps
(see also `data-raw/DATASET.R`)
(see also `get_ideea_map` function in `R/data.R`)
```{r, eval=FALSE}
# the script is a log of changes - do not rerun
library(tidyverse)
library(sf)
(load("data-raw/maps/ideea_r36o13.RData"))
(load("data-raw/maps/india_r46_sf.RData"))
ideea_r36o13
india_r46_sf

# create 37 region columns (split Daman & Diu) and save
if (F) { # (done - do not rerun)
  india_r46_sf <- india_r46_sf %>% 
    mutate(
      reg37 = if_else(reg46 %in% c("DM", "DU"), reg46, reg36),
      name37 = if_else(reg46 %in% c("DM", "DU"), name46, name36),
      .before = "reg36")
  save(india_r46_sf, file = "data-raw/maps/india_r46_sf.RData")
}


# create/save 37 region map with offshores 
# split offshore areas - ToDo later (!!!)
ideea_r36o13[ideea_r36o13$offshore, "reg36_off"] %>% plot()
ideea_r36o13$reg36_off %>% unique()

# split offshore regions (o13) to unique polygons
x <- ideea_r36o13[ideea_r36o13$offshore, "reg36_off"] %>% st_cast("POLYGON")
x <- x %>% mutate(n = as.factor(1:n())) 
x %>% select(n) %>% 
  plot(border = NA, axes = T, reset = F)
plot(x[3,], col = "red", border = "red", add = T, lwd = 4)
x %>% st_area() %>% as.numeric()/1e9

ii <- st_nearest_feature(india_r46_sf$geometry, x$geometry)
cc <- st_distance(india_r46_sf$geometry, x$geometry)
Rfast::rowMins(cc)
mm <- Rfast::colMins(cc)

# dd <- st_distance(x$geometry, india_r46_sf$geometry)
# dim(dd)
# rm <- Rfast::rowMins(dd)
# cm <- Rfast::colMins(dd)

# x$reg36_off
# india_r46_sf$reg46[rm]

# i <- 1
x$reg46 <- ""
india_r46_sf$n <- as.integer(NA)
for (i in 1:18) { # repeat for i in 1:18
  message(i)
  if (i == 4) mm[i] <- 35
  if (i == 8) mm[i] <- 9
  if (i == 13) mm[i] <- 33
  if (i == 14) {
    message(i, " several maches.. 37, 39, 43, assigning the first value")
    # !!! mm[i] <- c(37, 39, 43)
    mm[i] <- c(37) #, 39, 43
  } 
  # i <- 18 - ok
  plot(x["n"], reset = F)
  # plot(x[i, "n"], reset = F)
  plot(x$geometry[i], add = T, border = "red", lwd = 3)
  plot(india_r46_sf$geometry[mm[i]], add = T, col = "red")
  # plot(india_r46_sf$geometry[43], add = T, col = "blue", border = "blue", lwd = 3)
  # assign if correct
  x$reg46[i] <- india_r46_sf$reg46[mm[i]]
  # x$reg46[i] <- paste(x$reg46[i], india_r46_sf$reg46[mm[i]], sep = ",")
  india_r46_sf$n[mm[i]] <- mm[i]
  # i <- i + 1
}

on_r46 <- india_r46_sf %>% select(1:mainland) %>%
  mutate(offshore = F, .after = "mainland")
off_r46 <- x %>% select(reg46, geometry) %>%
  group_by(reg46) %>% summarise() %>% # combine split polygons of the same region
  left_join(st_drop_geometry(on_r46)) %>%
  mutate(offshore = T) %>%
  select(all_of(names(on_r46))) 
ideea_r46 <- rbind(on_r46, off_r46) 
unique(ideea_r46$reg46)
summary(ideea_r46$offshore)
# ideea_r46o15_sf <- ideea_r46
ideea_r46 <- ideea_r46 %>%
  mutate(
    reg1 = "IND", name1 = "India", .before = "mainland"
  )

plot(ideea_r46[1])
plot(ideea_r46["reg37"])
plot(ideea_r46["reg36"])
plot(ideea_r46["reg34"])
plot(ideea_r46["reg32"])
plot(ideea_r46["reg7"])
plot(ideea_r46["reg5"])
plot(ideea_r46["reg1"])

ideea_r46o15_sf <- ideea_r46
dim(ideea_r46o15_sf)
save(ideea_r46o15_sf, file = "data-raw/maps/ideea_r46o15_sf.RData")

IDEEA.dev::ideea_maps$ROW
```

## sf and other dependencies
```{r}
usethis::use_package("sf", type = "depends")
usethis::use_package("dplyr")
usethis::use_pipe()
usethis::use_import_from("glue", c("glue"))

```

*2023-06-07:*  
* adding `growth` article   
* structure of `energy` article   
* re-arranging articles menu (see `_pkgdown.yml`)   
* adding transmission network templates to google-doc  

```{r}
usethis::use_article("growth", "Growth and demand scenarios")

```

*2023-06-27:*  
* import functions from Google Sheets (in progress)
* adding `india_r36_sf` (see the script below)
```{r, eval=FALSE}
load("data-raw/maps/india_r46_sf.RData")
india_r36_sf <- india_r46_sf %>%
  group_by(reg36, name36) %>%
  summarise(
    geometry = globalwindatlas:::gwa_union_polygons(geometry, grid_size = 0),
    .groups = "drop"
  )
india_r36_sf
plot(india_r36_sf[1])

save(india_r36_sf, file = "data-raw/maps/india_r36_sf.RData")

# add offshore areas (from GWA)
library(globalwindatlas)
library(terra)
gwa_get_dir()
gwa_set_dir("../globalwindatlas/data/gwa")
gwa_tif <- gwa_get_wind_cf("IND")
gwa_rast <- rast(gwa_tif)
gwa_vc <- gwa_rast %>% terra::as.polygons() %>%
          terra::makeValid() %>% terra::aggregate()
plot(gwa_vc)
gwa_sf <- st_as_sf(gwa_vc)

row_sf <- IDEEA.dev::ideea_maps$ROW$ROW$sf
# row_buf_sf <- st_buffer(row_sf, .01, nQuadSegs = 300, endCapStyle = "ROUND")
row_buf_sf <- vect(row_sf) %>% terra::buffer(width = 1e4) %>% st_as_sf() %>%
  st_make_valid()
# plot(row_buf_sf)
plot(row_buf_sf[1], reset = F, col = "red")
plot(row_sf[1], add = T)

offshore_sf <- st_difference(gwa_sf, st_union(india_r36_sf)) %>% 
  st_make_valid() %>% globalwindatlas:::gwa_union_polygons()
offshore_sf <- st_difference(offshore_sf, st_make_valid(st_union(row_sf))) %>%
  globalwindatlas:::gwa_union_polygons()
offshore_sf <- st_difference(st_make_valid(offshore_sf),
                             st_make_valid(st_union(row_buf_sf$geometry))) 
offshore_sf %>% plot(col = "red")
st_bbox(offshore_sf)

bx <- matrix(c(60, 20, 75, 20, 75, 28, 60, 28, 60, 20), ncol = 2, byrow = T)
bx_sf <- st_polygon(x = list(bx)) %>% st_sfc() %>% st_as_sf() %>% 
  st_set_crs(st_crs(offshore_sf))

st_snap(offshore_sf, bx_sf)

smoothr::drop_crumbs(offshore_sf, 1e8) %>% plot()

offshore_sf <- smoothr::drop_crumbs(offshore_sf, 1e8)
st_bbox(offshore_sf)
save(offshore_sf, file = "data-raw/maps/offshore_sf.RData")

gis34_sf <- IDEEA.dev::ideea_maps$r34$with_offshores$sf
gwa_off_sf <- offshore_sf %>% st_as_sf %>% st_transform(st_crs(gis34_sf))

gis34_sf[1] %>% plot(col = NA, border = "blue")
gwa_off_sf %>% plot(col = NA, border = "red", add = T)

# library(tidyverse)
ggplot() +
  geom_sf(data = gis34_sf) +
  geom_sf(data = gwa_off_sf, fill = NA, color = "red")

# regionalize 
a <- st_transform(india_r36_sf, 32614) # crs may also affect results
# a <- st_transform(gis34_sf, 32722)
plot(a[1], axes = T)

library(cartomisc)
b <- regional_seas(a, "reg36", dist = units::set_units(300, km), 
                   # adjust and repeat several times (results depend on sampling)
                   # to get desirable outcome
                   density = units::set_units(0.05, 1/km) 
                   ) %>%
  st_transform(st_crs(gwa_off_sf))
plot(b[1])

d <- st_intersection(gwa_off_sf, st_make_valid(b)) %>% 
  st_make_valid(s2_options = s2::s2_options(snap = s2::s2_snap_precision(0), ...))
plot(d)
 
#
off_36_sf <- st_transform(d, st_crs(gis34_sf)) %>% st_make_valid() %>%
  rename(geometry = x) %>% mutate(offshore = TRUE, .before = "geometry")
land_36_sf <- st_transform(india_r36_sf, st_crs(gis34_sf)) %>% 
  st_make_valid() %>% mutate(offshore = FALSE, .before = "geometry") %>%
  select(-name36)


x <- st_difference(off_36_sf, land_36_sf) %>% select(reg36, offshore, geometry)

(load("~/R/IDEEA.dev/data-raw/maps/india_r46_sf.RData"))
y <- st_drop_geometry(india_r46_sf) %>% select(reg36, name36) %>% unique()
ii <- !(y$reg36 %in% land_36_sf$reg36)
y$reg36[ii]

# x <- x %>%
st_is_valid(x) %>% all()
plot(x[1])
off_36_sf <- x

gis_36_off <- rbind(land_36_sf, off_36_sf)
gis_36_off <- gis_36_off %>% left_join(y) %>% 
  select(reg36, name36, offshore, geometry) %>%
  mutate(
    reg36_off = if_else(offshore, paste0(reg36, "_off"), reg36),
    .after = "offshore"
  )

plot(gis_36_off[1])
plot(gis_36_off["reg36_off"])

# library(ggplot2)
g <- ggplot(gis_36_off) +
  geom_sf(aes(fill = reg36), color = alpha("black", .25)) +
  scale_fill_viridis_d(option = "H") +
  theme_bw()
ggsave("tmp/gis_36_off.png", plot = g, scale = 2, width = 7, height = 8)

ideea_r36o13 <- gis_36_off
save(ideea_r36o13, file = "data-raw/maps/ideea_r36o13.RData")

# g <- ggplot(gis_36_off) +
#   geom_sf(aes(fill = reg36), color = alpha("black", .25)) +
#   scale_fill_viridis_d(option = "H") +
#   theme_bw()
# ggsave("tmp/gis_36_off.png", plot = g, scale = 2, width = 7, height = 8)


# globalwindatlas:::gwa_union_polygons

# # split-area regions
# ii <- sapply(india_r36_sf$geometry, function(x) inherits(x, "MULTIPOLYGON"))
# summary(ii)
# 
# x <- india_r36_sf[ii,]
# x
# 
# plot(india_r36_sf[1], reset = F, color = NA)
# plot(x[x$reg36 == "PY", 1], axes = T, add = T, color = "red")


```


*2023-05-01:*  
* arranging articles menu (see `_pkgdown.yml`)   
* adding `ccus` article   
* adding `energy` article   
* `team.Rmd` renamed to `about.Rmd`   
* Google sheets, model input data: 
<https://docs.google.com/spreadsheets/d/1LF6aBkFF0o3tq-9l5OglL8A4eukG_en2pVQS7VKb23c/edit?usp=sharing>


```{r}
usethis::use_article("ccus", "Carbon capture, utilisation and storage")
usethis::use_article("energy", "Energy supply and trade")

```



*2023-04-19:*  
* ideea_r46_sf map is saved in the package internal files   
* logo added   
* website drafted   
* license changed to AGPL-3   
* + iron and steel sector
* + data article
* + 


```{r}
# IDEEA.dev::ideea_maps
library(sf)
(load("data-raw/maps/india_r46_sf.RData"))
plot(india_r46_sf["reg46"])
usethis::use_data(india_r46_sf, internal = TRUE)

# logo: "man/figures/logo.png"
# favicons (https://pkgdown.r-lib.org/reference/build_home.html):
# see pkgdown/favicon/
pkgdown::init_site()
usethis::use_agpl3_license()
usethis::use_vignette("iron_steel", "Iron and Steel sector")
usethis::use_article("install", "Installation")
usethis::use_article("team", "IDEEA team and community")
usethis::use_article("data", "IDEEA model open datasets")
usethis::use_r("data")

```



*2023-03-29:* 
* added LHDV to `transportation`  
* added `Karnataka` document (empty)   

```{r}
usethis::use_article("karnataka")

```


*2023-03-22:* 
* added `electricity` vignette // alternative name `power_sector`   
* added `hydrogen` vignette  
* added `transportation` vignette  
* added `buildings` vignette   

The website/package structure:  
vignettes: the model modules  
articles: desc/details on how data and/or particular modules have been assembled/processed  

```{r}
usethis::use_vignette("electricity")
usethis::use_vignette("hydrogen")
usethis::use_vignette("transportation")
usethis::use_vignette("buildings")

```


*2023-03-15:* 
* Updated `winddata` article with an example 


*2023-03-01:* 
* Adding the website using `pkgdown` tools   
https://pkgdown.r-lib.org/ 
```{r, eval=FALSE}
# log/reference only, no need to rerun
# usethis::use_pkgdown(config_file = "_pkgdown.yml", destdir = "docs")
usethis::use_pkgdown()
# to build the website
devtools::build_readme()
# library(pkgdown)
# pkgdown::clean_site()
# options(rmarkdown.html_vignette.check_title = FALSE)
# devtools::install(build_vignettes = TRUE)
pkgdown::build_site()
```
* Adding `dev/build.Rmd` to build or further edit the manual website.


*2023-02-27:* 
Renaming names of regions.  
(already don, the code is for reference)  

_renaming rules:_  
ideea_1r -> ideea_r1        # one region
ideea_5r3 -> ideea_r5o3     # 5 land and 3 offshore regions
ideea_7r_off -> deea_r7o5   # 7 land and 5 offshore regions

```{r, eval=FALSE}
library(sp)
library(sf)
library(stringr)
library(tidyverse)
# list all files
pth <- "data-raw/maps"
fls <- list.files(pth, pattern = "^ideea", full.names = F)
# rename initial files to delete later
for (i in 1:length(fls)) {
  file.rename(file.path(pth, fls[i]), file.path(pth, paste0("_", fls[i])))
}

# list files to rename them
fls <- list.files(pth, pattern = "^_ideea", full.names = T)
# i <- 2
for (i in 1:length(fls)) {
  cat(basename(fls[i]))
  (ff <- load(fls[i]))
  # f <- ff[1]
  nms <- ""
  for (j in 1:length(ff)) {
    mp <- get(ff[j])
    nr <- str_extract(ff[j], pattern = "[0-9]+r") %>% str_replace("r", "") # number of regions
    ni <- str_extract(ff[j], pattern = "ri") %>% str_replace("r", "") # number of regions
    no <- str_extract(ff[j], pattern = "r[0-9]+") %>% str_replace("r", "") # number of offshore
    off <- str_extract(ff[j], pattern = "off") # offshore
    try({id <- if_else(!is.null(mp$locid), "_locid", "")}, silent = T)
    if (inherits(id, "try-error")) id <- ""
    if (!is.na(off) & is.na(no)) {
      no <- length(unique(mp$reg_off[grepl("off", mp$reg_off)]))
    }
    rw <- str_extract(ff[j], pattern = "row") # rest of the world
    cl <- str_extract(ff[j], pattern = "sf$|sp$") # class of the object
    nn <- "ideea" # new name
    if (!is.na(nr)) nn <- paste0(nn, "_r", nr) # new name
    if (!is.na(ni)) nn <- paste0(nn, "i")
    if (!is.na(no)) nn <- paste0(nn, "o", no)
    nn <- paste0(nn, id)
    if (!is.na(rw)) nn <- paste0(nn, "_row")
    fname <- paste0(nn, ".RData")
    nn <- paste0(nn, "_", cl)
    nms[j] <- nn
    assign(nn, get(ff[j]))
    rm(mp)
  }
  cat(" -> ", fname, "\n")
  stopifnot(!file.exists(file.path(pth, fname)))
  save(list = nms, file = file.path(pth, fname))
}
unlink(fls)
(load("data-raw/maps/_india_46r_sf.RData"))
india_r46_sf <- india_46r_sf
save(india_r46_sf, file = "data-raw/maps/india_r46_sf.RData")
unlink("data-raw/maps/_india_46r_sf.RData")

```

_ideea_1r.RData ->  ideea_r1.RData 
_ideea_1ri.RData ->  ideea_r1i.RData 
_ideea_32r.RData ->  ideea_r32.RData 
_ideea_32r_off.RData ->  ideea_r32o11_locid.RData 
_ideea_32r_row.RData ->  ideea_r32_row.RData 
_ideea_32r11.RData ->  ideea_r32o11.RData 
_ideea_34r.RData ->  ideea_r34.RData 
_ideea_34r_off.RData ->  ideea_r34o12_locid.RData 
_ideea_34r_row.RData ->  ideea_r34_row.RData 
_ideea_34r11.RData ->  ideea_r34o11.RData 
_ideea_5r.RData ->  ideea_r5.RData 
_ideea_5r_off.RData ->  ideea_r5o3_locid.RData 
_ideea_5r3.RData ->  ideea_r5o3.RData 
_ideea_7r.RData ->  ideea_r7.RData 
_ideea_7r_off.RData ->  ideea_r7o5_locid.RData 
_ideea_7r5.RData ->  ideea_r7o5.RData 
_ideea_row.RData ->  ideea_row.RData 

```{r, eval=FALSE}
ideea_maps <- list(
  "r1" = list(
    "mainland" = 
      list(
        "sf" = ideea_r1_sf,
        "sp" = ideea_r1_sp),
    "with_islands" = 
      list(
        "sf" = ideea_r1i_sf,
        "sp" = ideea_r1i_sp)
      )
  )

# 5 regions ####
(load("data-raw/maps/ideea_r5.RData"))
plot(ideea_r5_sf[1])

(load("data-raw/maps/ideea_r5o3_locid.RData"))
plot(ideea_r5o3_locid_sf[1])

ideea_maps[["r5"]] <- list(
    "land" = 
      list(
        "sf" = ideea_r5_sf,
        "sp" = ideea_r5_sp),
    "with_offshores" = 
      list(
        "sf" = ideea_r5o3_locid_sf,
        "sp" = ideea_r5o3_locid_sp)
      )
names(ideea_maps)
names(ideea_maps$`r5`$with_offshores)

# 7 regions ####
(load("data-raw/maps/ideea_r7.RData"))
plot(ideea_r7_sf[1])

(load("data-raw/maps/ideea_r7o5_locid.RData"))
plot(ideea_r7o5_locid_sf[1])

ideea_maps[["r7"]] <- list(
  "land" = 
    list(
      "sf" = ideea_r7_sf,
      "sp" = ideea_r7_sp),
  "with_offshores" = 
    list(
      "sf" = ideea_r7o5_locid_sf,
      "sp" = ideea_r7o5_locid_sp)
)
names(ideea_maps)
names(ideea_maps$r7$with_offshores)

# 32 regions ####
(load("data-raw/maps/ideea_r32.RData"))
plot(ideea_r32_sf[1])

(load("data-raw/maps/ideea_r32o11.RData"))
plot(ideea_r32o11_sf[1])

(load("data-raw/maps/ideea_r32o11_locid.RData"))
plot(ideea_r32o11_locid_sf[1])

(load("data-raw/maps/ideea_r32_row.RData"))
plot(ideea_r32_row_sf[1])

ideea_maps[["r32"]] <- list(
  "land" = 
    list(
      "sf" = ideea_r32_sf,
      "sp" = ideea_r32_sp),
  "with_offshores" = 
    list(
      "sf" = ideea_r32o11_sf,
      "sp" = ideea_r32o11_sp),
    # list(
    #   "sf" = ideea_32r_off_sf,
    #   "sp" = ideea_32r_off_sp),
  "with_ROW" = 
    list(
      "sf" = ideea_r32o11_locid_sf,
      "sp" = ideea_r32o11_locid_sp)
)
names(ideea_maps)
names(ideea_maps$r32$with_offshores)

# 34 regions ####
(load("data-raw/maps/ideea_r34.RData"))
plot(ideea_r34_sf[1])

(load("data-raw/maps/ideea_r34o11.RData"))
plot(ideea_r34o11_sf[1])

(load("data-raw/maps/ideea_r34o12_locid.RData"))
plot(ideea_r34o12_locid_sf[1])

(load("data-raw/maps/ideea_r34_row.RData"))
plot(ideea_r34_row_sf[1])

ideea_maps[["r34"]] <- list(
  "land" = 
    list(
      "sf" = ideea_r34_sf,
      "sp" = ideea_r34_sp),
  "with_offshores" = 
    list(
      "sf" = ideea_r34o11_sf,
      "sp" = ideea_r34o11_sp),
  # list(
  #   "sf" = ideea_34r_off_sf,
  #   "sp" = ideea_34r_off_sp),
  "with_ROW" = 
    list(
      "sf" = ideea_r34o12_locid_sf,
      "sp" = ideea_r34o12_locid_sp)
)
names(ideea_maps)
names(ideea_maps$r34$with_offshores)



# 46 regions and subregions/territories ####
# (load("data-raw/maps/india_46r_sf.RData"))
# plot(india_46r_sf[1])
# ideea_maps[["46r"]] <- list(
#   "land" = 
#     list(
#       "sf" = india_46r_sf)
# )
# ROW ####
(load("data-raw/maps/ideea_row.RData"))
plot(ideea_row_sf[1])
ideea_maps[["ROW"]] <- list(
  "ROW" =
    list(
      "sf" = ideea_row_sf,
      "sp" = ideea_row_sp
      )
)
names(ideea_maps)

# * Saving data file ("sysdata.rda")
usethis::use_data(ideea_maps, internal = FALSE) # overwrite = T)

```



*2023-02-17:* 
Adding *maps* article...
ToDo: rename maps - from `1r` to `r1` etc. for better accessibility.  
```{r, eval=FALSE}
usethis::use_article("maps")

```


*2022-03-29:* 
* **GitHub** private repository <https://github.com/ideea-model/IDEEA.dev> to develop and test the IDEEA model package; the temporary/development name of the package is **IDEEA.dev**.  
* Creating the package infrastructure using *devtools*. See <https://r-pkgs.org> for details.  
```{r, eval=FALSE}
# Do Not Run! This chunk is for reference only.
# <https://r-pkgs.org/whole-game.html>
library(devtools)
packageVersion("devtools")
?create_package()
?create_tidy_package()
create_tidy_package(getwd())
# dialogue selections:
# overwrite? ... yes... yes

```

* Create dataset  
```{r, eval=FALSE}
# external dataset that will not be included to the package, but used to create data for the package
## create the folder
usethis::use_data_raw()
# maps: 
## copy/paste (by hand) maps from in IDEEA R-project
list.files("data-raw/maps")
#  [1] "ideea_1r.RData"      "ideea_1ri.RData"     "ideea_32r.RData"     "ideea_32r_off.RData"
#  [5] "ideea_32r_row.RData" "ideea_32r11.RData"   "ideea_34r.RData"     "ideea_34r_off.RData"
#  [9] "ideea_34r_row.RData" "ideea_34r11.RData"   "ideea_5r.RData"      "ideea_5r_off.RData" 
# [13] "ideea_5r3.RData"     "ideea_7r.RData"      "ideea_7r_off.RData"  "ideea_7r5.RData"    
# [17] "ideea_row.RData"     "india_46r_sf.RData" 

# add maps to the package's data
library(sp)
library(sf)
# 1 region ####
(load("data-raw/maps/ideea_1r.RData"))
plot(ideea_1r_sf)

load("C:/Users/Sourish/Desktop/git_repository/IDEEA.dev/data-raw/maps/ideea_1ri.RData")
(load("data-raw/maps/ideea_1ri.RData"))
plot(ideea_1ri_sf)

ideea_maps <- list(
  "1r" = list(
    "mainland" = 
      list(
        "sf" = ideea_1r_sf,
        "sp" = ideea_1r_sp),
    "with_islands" = 
      list(
        "sf" = ideea_1ri_sf,
        "sp" = ideea_1ri_sp)
      )
  )
# 5 regions ####
(load("data-raw/maps/ideea_5r.RData"))
plot(ideea_5r_sf[1])

(load("data-raw/maps/ideea_5r_off.RData"))
plot(ideea_5r_off_sf[1])

ideea_maps[["5r"]] <- list(
    "land" = 
      list(
        "sf" = ideea_5r_sf,
        "sp" = ideea_5r_sp),
    "with_offshores" = 
      list(
        "sf" = ideea_5r_off_sf,
        "sp" = ideea_5r_off_sp)
      )
names(ideea_maps)
names(ideea_maps$`5r`$with_offshores)

# 7 regions ####
(load("data-raw/maps/ideea_7r.RData"))
plot(ideea_7r_sf[1])

(load("data-raw/maps/ideea_7r_off.RData"))
plot(ideea_7r_off_sf[1])

ideea_maps[["7r"]] <- list(
  "land" = 
    list(
      "sf" = ideea_7r_sf,
      "sp" = ideea_7r_sp),
  "with_offshores" = 
    list(
      "sf" = ideea_7r_off_sf,
      "sp" = ideea_7r_off_sp)
)
names(ideea_maps)
names(ideea_maps$`7r`$with_offshores)

# 32 regions ####
(load("data-raw/maps/ideea_32r.RData"))
plot(ideea_32r_sf[1])

(load("data-raw/maps/ideea_32r11.RData"))
plot(ideea_32r11_sf[1])

(load("data-raw/maps/ideea_32r_off.RData"))
plot(ideea_32r_off_sf[1])

(load("data-raw/maps/ideea_32r_row.RData"))
plot(ideea_32r_row_sf[1])

ideea_maps[["32r"]] <- list(
  "land" = 
    list(
      "sf" = ideea_32r_sf,
      "sp" = ideea_32r_sp),
  "with_offshores" = 
    list(
      "sf" = ideea_32r11_sf,
      "sp" = ideea_32r11_sp),
    # list(
    #   "sf" = ideea_32r_off_sf,
    #   "sp" = ideea_32r_off_sp),
  "with_ROW" = 
    list(
      "sf" = ideea_32r_off_sf,
      "sp" = ideea_32r_off_sp)
  
)
names(ideea_maps)
names(ideea_maps$`32r`$with_offshores)

# 34 regions ####
(load("data-raw/maps/ideea_34r.RData"))
plot(ideea_34r_sf[1])

(load("data-raw/maps/ideea_34r11.RData"))
plot(ideea_34r11_sf[1])

(load("data-raw/maps/ideea_34r_off.RData"))
plot(ideea_34r_off_sf[1])

(load("data-raw/maps/ideea_34r_row.RData"))
plot(ideea_34r_row_sf[1])

ideea_maps[["34r"]] <- list(
  "land" = 
    list(
      "sf" = ideea_34r_sf,
      "sp" = ideea_34r_sp),
  "with_offshores" = 
    list(
      "sf" = ideea_34r11_sf,
      "sp" = ideea_34r11_sp),
  # list(
  #   "sf" = ideea_34r_off_sf,
  #   "sp" = ideea_34r_off_sp),
  "with_ROW" = 
    list(
      "sf" = ideea_34r_off_sf,
      "sp" = ideea_34r_off_sp)
  
)
names(ideea_maps)
names(ideea_maps$`34r`$with_offshores)



# 46 regions and subregions/territories ####
# (load("data-raw/maps/india_46r_sf.RData"))
# plot(india_46r_sf[1])
# ideea_maps[["46r"]] <- list(
#   "land" = 
#     list(
#       "sf" = india_46r_sf)
# )
# ROW ####
(load("data-raw/maps/ideea_row.RData"))
plot(ideea_row_sf[1])
ideea_maps[["ROW"]] <- list(
  "ROW" =
    list(
      "sf" = ideea_row_sf,
      "sp" = ideea_row_sp
      )
)
names(ideea_maps)

```

* Saving data file ("sysdata.rda")
```{r, eval=FALSE}
usethis::use_data(ideea_maps, internal = FALSE)


```

* Dependencies
```{r, eval=FALSE}
usethis::use_package("energyRt", "Depends")


```

# Vignettes and articles
## Getting started
```{r}
usethis::use_vignette("IDEEA")

usethis::use_article("winddata", "Building wind database")

```


## 1-region model
```{r, eval=FALSE}
usethis::use_article("ideea-1r")


```



