---
title: "Building wind database"
params: 
  yaml_path: "config" # directory with YAML file
  iso3c: IND # country code
  wyear: 2014 # weather year
  win_onshore_MW_km2: 4 # assumption (see info), maximum MW per km2
  win_offshore_MW_km2: 4 # assumption (see info), maximum MW per km2
  win_gwa_cf_min: 0.2 # lowest capacity factor in Global Wind Atlas, class 2
  win_merra_cf_min: 0.1 # lowest capacity factor according to MERRA2 (`waf100m`)
  win_cl_max: 100 #  maximum number of clusters of wind-data per region
  win_cl_tol: .05 # maximum loss of s.d. in selection of number of clusters
  sol_onshore_MW_km2: 80 # assumption (see info), maximum MW per km2
  sol_offshore_MW_km2: 0 # assumption (see info), maximum MW per km2
  sol_cl_max: 100 # maximum number clusters of solar-data per region
  sol_cl_tol: .01 # maximum loss of s.d. in selection of number of clusters
  reimport_merra: false # if true, saved merra and pre-processed data won't be used
  reimport_gwa: false # if true, redo GWA groupping
  recluster_win: true # ignore previously saved clustering with the same parameters
  recluster_sol: true # ignore previously saved clustering with the same parameters
  # echo: true # show R-script in reports
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(IDEEA.dev)
library(merra2ools)
library(data.table)
library(fst)
library(globalwindatlas)
# library(terra)
library(sp)
library(sf)
library(glue)

# map 
# gis_sp0 <- IDEEA.dev::ideea_maps$r32$with_offshores$sp
# gis_sf <- IDEEA.dev::ideea_maps$r32$with_offshores$sf %>%
#   mutate(
#     region = reg32,
#     .before = 1
#   )

# wyear <- 2014
dir.create("data-raw/merra", showWarnings = F)
gis_sf <- get_ideea_map(36, offshore = T, islands = T, ROW = F)

tzone <- "Asia/Kolkata"
with_tz(now(), tzone)

wyear <- params$wyear

# cluster-version identifier to add to names of capacity factors 
# to distinguish alternative versions of clusters
win_cl_mask <- 
  glue(
    "CL", params$win_cl_max, # max allowed number of clusters
    "_TOL", prettyNum(params$win_cl_tol) # loss/tolerance
  ) %>% 
  str_replace_all("\\.", "")

sol_cl_mask <- 
  glue(
    "CL", params$sol_cl_max, # max allowed number of clusters
    "_TOL", prettyNum(params$sol_cl_tol) # loss/tolerance
  ) %>% 
  str_replace_all("\\.", "")

```

<!-- ## Wind potential (250m) map -->
<!-- ```{r, eval=FALSE} -->
<!-- if(dir.exists("tmp/data/gwa")) dir.create("tmp/data/gwa") -->
<!-- gwa_set_dir("tmp/data/gwa") -->
<!-- file_iec <- gwa_get_wind_cf("IND", IEC = 2) -->
<!-- obj0_tr <- rast(file_iec) -->
<!-- plot(obj0_tr) -->
<!-- ``` -->


## Locations
```{r}
# library(merra2ools)
# gis_sf <- get_ideea_map(36, offshore = T, islands = T, ROW = F)
locid_all <- get_locid(gis_sf)
length(locid_all)

# if (T) { # temproary solution - fix later
#   (load("tmp/locid_tot.RData"))
#   # locid_all <- locid_tot
#   length(locid_tot); length(locid_all)
#   all(locid_all %in% locid_tot)
# }

locid_grid_sf <- get_merra_grid("poly", locid = locid_all) %>%
  select(locid) %>%
  left_join(merra2ools::mean_cf) %>%
  # left_join(select(merra2ools::merra2_cor_W50M, locid, Z)) %>%
  st_make_valid()
locid_grid_sf %>% dim()


fig_fname <- file.path("tmp", glue("locid_grid_sf-saf_fl.png"))
ggplot() + 
  geom_sf(aes(fill = saf_fl), data = locid_grid_sf) +
  scale_fill_viridis_c(option = "A") +
  geom_sf(data = gis_sf, fill = NA, color = "black") +
  theme_bw()
ggsave(fig_fname, scale = 1.5, height = 5, width = 6)

```

```{r}
ggplot() + 
  geom_sf(aes(fill = waf100m), data = locid_grid_sf) +
  scale_fill_viridis_c(option = "D") +
  geom_sf(data = gis_sf, fill = NA, color = "white") +
  # geom_sf(data = gis$adm1$sf, fill = NA, color = "white") +
  theme_bw()
ggsave("tmp/win_cf_100m.png", scale = 1.5, height = 6, width = 5)

```


## MERRA2 subset
```{r, eval=TRUE}
fname <- file.path("data-raw/merra", glue("merra_raw_{wyear}.fst"))
if (!file.exists(fname) | params$reimport_merra) {
  message("Importing data from MERRA2 database, ", length(locid_all),
          " locations, ", params$wyear, " year")
  merra <- get_merra2_subset(locid = locid_all, 
                             from = fDate(wyear, 01, 01, 0), 
                             to = fDate(wyear, 12, 31, 23),
                             tz = "UTC")
  merra <- merra %>% select(UTC, locid, W10M, W50M, SWGDN, ALBEDO)
  message("Saving 'raw' data: ", fname)
  fst::write_fst(merra, fname, compress = 100)
  cat("File size:", {file.size(fname) %>% gdata::humanReadable()})
  # save(merra, 
  #      file = file.path("data-raw/merra", glue("merra_raw_{wyear}.RData")))
} else {
  message("Reading MERRA2 subset: ", fname)
  merra <- read_fst(fname, as.data.table = T)
}
```

## Wind
Process MERRA2 data (subset) to estimate hourly wind capacity factors and group locations.

### Capacity factors
```{r, eval=TRUE}
merra_wind <- merra %>% 
  # fPOA() %>% # solar (POA)
  fWindCF(50, return_name = "wcf50m") %>% # wind
  fWindCF(100, return_name = "wcf100m") %>%
  fWindCF(150, return_name = "wcf150m") %>%
  select("UTC", "locid", starts_with("wcf"))
```

### Filter locations
Using Global Wind Atlas high-resolution maps of wind potential, filter locations with high wind capacity factors. 

```{r}
library(terra)
library(globalwindatlas)

# gwa_set_dir(file.path(p$dir$data, "gwa"))
gwa_set_dir("tmp/data/gwa")
gwa_get_dir()
gwa_tif <- gwa_get_wind_cf("IND", IEC = 2) # wind-class #2

## plot 
gwa_rast <- rast(gwa_tif)
plot(gwa_rast, main = "Wind capacity factors")

# summary(tr)
# gis_sf <- gis_sf
# plot(gis_sf[1])
```

```{r}
fname <- file.path("tmp/data/gwa", "gwa_iec2_sf.RData")
if (!file.exists(fname) | params$reimport_gwa) {
  # gwa_tif2 <- terra::aggregate(gwa_tif)
  gwa_iec2_sf <- gwa_group_locations(gwa_tif, 
                                     gis_sf, 
                                     aggregate_tif = 0, 
                                     drop_crumps = 100,
                                     simplify = 0.001,
                                     buffer = 0,
                                     int = seq(0, 1, by = .1), 
                                     verbose = T)
  save(gwa_iec2_sf, file = fname)
} else {
  load(fname)
}
rm(fname)
# installr::os.sleep(first_turn_hibernate_off = F)
ggplot(gwa_iec2_sf) +
  geom_sf(aes(fill = eq), color = NA) +
  # geom_sf(color = "grey", fill = NA, data = gis$voronoi$sf) +
  scale_fill_viridis_d(option = "H", direction = 1, name = "CF") +
  theme_bw()
ggsave("gwa_iec2_sf.png", path = "tmp", height = 6, width = 5, scale = 1.5)

# size <- energyRt::size
# energyRt::size(gwa_iec2_sf)
# gwa_iec2_sf_sim <- st_simplify(gwa_iec2_sf, dTolerance = 1e3)
# energyRt::size(gwa_iec2_sf_sim)
# ggplot(gwa_iec2_sf_sim) +
#   geom_sf(aes(fill = eq), color = NA) +
#   # geom_sf(color = "grey", fill = NA, data = gis$voronoi$sf) +
#   scale_fill_viridis_d(option = "H", direction = 1, name = "CF") +
#   theme_bw()
# 
# gwa_iec2_sv <- vect(gwa_iec2_sf)
# size(gwa_iec2_sv)
# gwa_iec2_sv_buf <- terra::buffer(gwa_iec2_sv, 100)
# size(gwa_iec2_sv_buf)
# 
# 
# gwa_iec2_sf_sim2 <- terra::simplifyGeom(vect(gwa_iec2_sf))
# energyRt::size(gwa_iec2_sf_sim2)
# gwa_iec2_sf_sim <- st_as_sf(gwa_iec2_sf_sim2)
# 
# # select locations with higher than 20% 
# gwa_iec2_sf$int %>% unique()

locid_gwa_sf <- locid_grid_sf %>%
  st_make_valid() %>%
  st_intersection(
    filter(gwa_iec2_sf, int >= params$win_gwa_cf_min),
    dimensions = c("polygon")
  ) %>%
  st_make_valid() %>%
  mutate(
    area = units::set_units(st_area(geometry), "km^2"),
    MW_max = as.numeric(round(if_else(grepl("off", reg_off), 
                                      4 * area, 4 * area), 0)),
    .before = "geometry"
  )

ggplot(locid_gwa_sf) +
  geom_sf(color = alpha("black", .25), fill = "lightgrey", 
          data = gis_sf) +
  geom_sf(aes(fill = waf100m), color = NA) +
  scale_fill_viridis_c(option = "H", direction = 1, name = "waf100m") +
  labs(title = paste0("IDEEA, wind locations with cf >= ", 
                      params$win_gwa_cf_min, " (GWA)")) +
  theme_bw()
ggsave("locid_gwa_sf.png", path = "tmp", height = 6, width = 5, scale = 1)

locid_win_sf <- locid_gwa_sf %>%
  filter(waf100m > params$win_merra_cf_min)

ggplot(locid_win_sf) +
  geom_sf(color = alpha("black", .25), fill = "lightgrey", 
          data = gis_sf) +
  geom_sf(aes(fill = waf100m), color = NA) +
  scale_fill_viridis_c(option = "H", direction = 1, 
                       name = "CF 100m\n(MERRA)") +
  labs(title = paste0("IDEEA", ", filtered wind locations"),
       subtitle = glue(
          "GWA cf >= {params$win_gwa_cf_min},", 
          " MERRA cf >= {params$win_merra_cf_min}"
          )) +
  theme_bw()
ggsave("locid_win_sf.png", path = "tmp", height = 7, width = 6, scale = 1.5)

```

```{r}
locid_win_sf <- locid_win_sf %>%
  mutate(region = reg32, .after = "reg32")
```



### Cluster locations
```{r, eval=T}
fname <- file.path("tmp", glue("locid_win_cl.RData"))
if (!file.exists(fname) | params$recluster_win) {
  locid_win_cl <- 
    cluster_locid(merra_wind, 
                  varname = "wcf100m", 
                  locid_info = locid_win_sf, 
                  group = "reg_off", 
                  weight = "MW_max",
                  # k = 1:params$win_cl_max,
                  max_loss = .001,
                  verbose = T)
  message("Saving clustering results: ", fname)
  save(locid_win_cl, file = fname)
} else {
  load(fname)
}

# fname <- file.path("tmp", glue("locid_win_sf.RData"))
# locid_win_cl_sf <- locid_win_sf %>%
#   st_make_valid() %>%
#   left_join(
#     select(locid_win_cl, any_of(c("reg_off", "region", "locid", "cluster")))
#   ) %>%
#   filter(!is.na(cluster)) %>%
#   mutate(cluster = factor(cluster))
# save(locid_win_cl_sf, file = fname); rm(fname)


ggplot(locid_win_cl_sf) +
  geom_sf(fill = "lightgrey", data = gis_sf) +
  geom_sf(aes(fill = cluster), color = NA) +
  geom_sf(color = alpha("black", 1), fill = NA, data = gis_sf) +
  scale_fill_viridis_d(option = "D", direction = 1, name = "Cluster") +
  labs(title = paste0("Clustered wind sites by region")) +
  theme_bw()
ggsave("locid_win_cl_sf.png", path = "tmp", height = 5, width = 7, scale = 1)

```


### Aggregate  
**merra_win_cl** - hourly wind capacity factors, aggregated by clusters & regions.  
**win_GW_max_sf** - spatial data.frame by clusters & regions with estimated maximum installed capacity, based on surface area (see YAML-header parameters).  
```{r}
merra_win_cl <- merra_wind %>%
  filter(locid %in% unique(locid_win_cl$locid)) %>% # drop unused locations
  mutate(slice = timeslices::dtm2tsl(UTC)) %>% # create time-slice IDs
  select(locid, slice, wcf50m, wcf100m, wcf150m) %>% # drop unused columns
  right_join( # merge with gis-data
    select(st_drop_geometry(locid_win_cl_sf), 
           locid, region, reg_off, cluster, MW_max), 
    relationship = "many-to-many"
  ) %>%
  group_by(slice, region, reg_off, cluster) %>%
  summarise(
    wcf50m = round(weighted.mean(wcf50m, MW_max, na.rm = T), 3),
    wcf100m = round(weighted.mean(wcf100m, MW_max, na.rm = T), 3),
    wcf150m = round(weighted.mean(wcf150m, MW_max, na.rm = T), 3),
    .groups = "drop"
  ) %>%
  mutate(year = params$wyear, .before = 1) %>%
  select(-region) %>%
  as.data.table()
merra_win_cl

fname <- file.path("tmp", 
                   glue("merra_win_{win_cl_mask}_{wyear}.fst"))
message("Writing ", fname)
write_fst(merra_win_cl, fname, compress = 100); rm(fname)

win_GW_max_sf <- locid_win_cl_sf %>% 
  filter(MW_max > 0) %>%
  st_make_valid() %>%
  # st_drop_geometry() %>%
  # select(region, reg_off, offshore, cluster, MW_max) %>% 
  group_by(region, reg_off, cluster) %>% 
  reframe(
    wcf50m = weighted.mean(waf50m, MW_max, na.rm = T),
    wcf100m = weighted.mean(waf100m, MW_max, na.rm = T),
    wcf150m = weighted.mean(waf150m, MW_max, na.rm = T),
    # saf_fh = weighted.mean(saf_fh, MW_max, na.rm = T),
    # saf_ft = weighted.mean(saf_ft, MW_max, na.rm = T),
    # saf_tl = weighted.mean(saf_tl, MW_max, na.rm = T),
    # saf_td = weighted.mean(saf_td, MW_max, na.rm = T),
    area = sum(area, na.rm = T),
    win_GW_max = sum(MW_max, na.rm = T) / 1e3,
    geometry = st_union(
      st_as_sfc(
        s2::s2_snap_to_grid(geometry, grid_size = 1e-5))
      )
    # .groups = "drop"
  ) %>% st_as_sf() %>% st_make_valid()
fname <- file.path("tmp", glue("win_GW_max_{win_cl_mask}.RData"))
message("Saving ", fname)
save(win_GW_max_sf, file = fname); rm(fname)
plot(win_GW_max_sf["cluster"], border = NA)


# win_GW_max_sf <- locid_win_cl_sf %>%
#   filter(MW_max > 0) %>%
#   st_simplify(dTolerance = .001) %>%
#   st_make_valid() %>%
#   group_by(region, reg_off, offshore, cluster) %>% 
#   summarize()
#   
# 
# fname <- file.path("tmp", glue("win_GW_max_sf_{win_cl_mask}.RData"))
# save(win_GW_max_sf, file = fname); rm(fname)

if (!is.null(locid_win_cl_sf$MW_max)) {
  locid_win_cl_sf <- locid_win_cl_sf %>%
    rename(win_MW_max = MW_max)
}

win_GW_max_sf <- locid_win_cl_sf %>% 
  filter(win_MW_max > 0) %>%
  st_make_valid() %>%
  # select(region, reg_off, offshore, cluster, win_MW_max) %>% 
  group_by(region, reg_off, offshore, cluster) %>% 
  reframe(
    wcf50m = weighted.mean(wcf50m, win_MW_max, na.rm = T),
    wcf100m = weighted.mean(wcf100m, win_MW_max, na.rm = T),
    wcf150m = weighted.mean(wcf150m, win_MW_max, na.rm = T),
    area = sum(area, na.rm = T),
    win_GW_max = sum(win_MW_max, na.rm = T) / 1e3,
    geometry = rev_union_polygons(geometry)
  ) %>% 
  st_as_sf() %>% st_make_valid()

ggplot(win_GW_max_sf) +
  geom_sf(fill = "lightgrey", data = gis_sf) +
  geom_sf(aes(fill = .data[[p$win_cf]]), color = alpha("black", .5),) +
  scale_fill_viridis_c(option = "H", direction = 1) +
  labs(title = "Average wind capacity factors by cluster and region",
       subtitle = glue("sd_loss <= ", params$win_cl_tol * 100, 
                       "%, data: MERRA2, year: {wyear}")) +
  rev_theme_map()

```

## Solar 
Process MERRA2 subset to estimate hourly solar capacity factors, group and aggregate locations.

### Capacity factors
```{r, eval=FALSE}
merra_solar <- merra %>% 
  fPOA(array.type = c("fh", "fl", 
                      # "th", "tv", # rarely used & similar to other types
                      "tl", "td")) %>% # solar (Plain of Array irradiance)
  mutate(
    # simplified version of capacity factors, 
    # assuming pick of output when POA >= 1000 Watt/m^2
    scf_fh = round(POA.fh / 1e3, 3),
    scf_fl = round(POA.fl / 1e3, 3),
    # scf_th = round(POA.th / 1e3, 3),
    # scf_tv = round(POA.tv / 1e3, 3),
    scf_tl = round(POA.tl / 1e3, 3),
    scf_td = round(POA.td / 1e3, 3)
  ) %>%
  mutate(
    # curtail cf > 1 (when POA > 1kW/m^2)
    scf_fh = if_else(scf_fh > 1, 1, scf_fh),
    scf_fl = if_else(scf_fl > 1, 1, scf_fl),
    # scf_th = if_else(scf_th > 1, 1, scf_th),
    # scf_tv = if_else(scf_tv > 1, 1, scf_tv),
    scf_tl = if_else(scf_tl > 1, 1, scf_tl),
    scf_td = if_else(scf_td > 1, 1, scf_td)
  ) %>%
  select(locid, UTC, starts_with("scf_"))
# summary(merra_solar)

merra_solar
```

#### Cluster locations
```{r sol_cluster, eval=TRUE}
locid_sol_sf <- locid_grid_sf %>%
  st_make_valid() %>%
  st_intersection(st_make_valid(gis_sf)) %>%
  st_make_valid() %>%
  mutate(
    area = units::set_units(st_area(geometry), "km^2"),
    offshore = if_else(grepl("off", reg_off), T, F),
    sol_MW_max = as.numeric(round(if_else(
      offshore,
      params$sol_offshore_MW_km2 * as.numeric(area),
      params$sol_onshore_MW_km2 * as.numeric(area)), 0)),
    .before = "geometry"
  )

fname <- file.path("tmp", glue("locid_sol_cl.RData"))
if (!file.exists(fname) | p$sol_recluster) {
  # # number of clusters to consider
  # if (p$n_locid / p$nreg > 50) { 
  #   # reducing computation time of clusters by reducing the number of options
  #   p$sol_k_seq <- c(1:10, 12, 15, 20, 25, 35, 50, 70, 100, 150, 
  #                    seq(200, 1000, by = 100))
  # } else {
  #   p$sol_k_seq <- NULL # use default settings
  # }
  # cluster locations
  locid_sol_cl <- 
    cluster_locid(merra_solar, varname = "scf_tl", 
                  locid_info = locid_sol_sf,
                  group = "reg_off", 
                  weight = "sol_MW_max",
                  # k = 1:p$sol_cl_max,
                  max_loss = .00,
                  verbose = T)
  
  save(locid_sol_cl, file = fname)
} else {
  load(fname)
}
rm(fname)

p <- list(
  sol_cl_tol = 0.01,
  sol_cl_mask = "TOL001"
  )

# Select clusters based on parameters
locid_sol_cl_k <- locid_sol_cl %>% 
  filter(sd_loss <= p$sol_cl_tol) %>% 
  group_by(reg_off) %>% 
  mutate(k_min = (k == min(k))) %>% ungroup() %>% 
  filter(k_min) %>% select(-k_min) %>%
  as.data.table()

# Cluster-loss figure
locid_sol_cl_kk <- locid_sol_cl %>%
  group_by(reg_off, k) %>%
  summarise(sd_loss = max(sd_loss), N = max(N), .groups = "drop")

locid_sol_cl_k_i <- locid_sol_cl_k %>%
  group_by(reg_off, k) %>%
  summarise(sd_loss = max(sd_loss), N = max(N), .groups = "drop")

a <- ggplot(locid_sol_cl_kk) +
  geom_line(aes(k, sd_loss), color = "dodgerblue", linewidth = 1.5) +
  geom_point(aes(k, sd_loss), color = "red", data = locid_sol_cl_k_i) +
  scale_y_continuous(labels = scales::percent, limits = c(0, NA)) +
  scale_x_continuous(breaks = rev_integer_breaks(5)) +
  labs(x = "Number of clusters (k)", 
       y = "loss, % of s.d.",
       title = "Aggregation lossess by number of clusters") +
  facet_wrap(~paste0(reg_off, " (", N," locations)"), scales = "free",
             ncol = max(1, round(nrow(locid_sol_cl_k_i) / 5))) +
  rev_theme_map()

if (p$sol_cl_tol < 1) {
  a <- a + 
    geom_hline(aes(yintercept = p$sol_cl_tol), col = "red", linetype = 2) +
    labs(subtitle = glue("The red line and dots indicate tolerance (", 
                         100 * p$sol_cl_tol, "%) ",
                         "and selected number of clusters"))
} else {
  a <- a + 
    labs(subtitle = glue("Red points indicates selected number of clusters ",
                         "(tolerance <= ", 100 * p$sol_cl_tol, "%)"))
}
a
ggsave(glue("sol_cl_sd_loss_{sol_cl_mask}.png"), a, path = "tmp", 
       width = 6, height = 8, scale = 1.25)

fname <- file.path(p$dir$data_mod, glue("locid_sol_cl_sf_{sol_cl_mask}.RData"))
locid_sol_cl_sf <- locid_sol_sf %>%
  st_make_valid() %>%
  left_join(
    select(locid_sol_cl_k, any_of(c("reg_off", "region", "locid", "cluster")))
  ) %>%
  filter(!is.na(cluster)) %>%
  mutate(cluster = factor(cluster))
save(locid_sol_cl_sf, file = fname); rm(fname)

ggplot(locid_sol_cl_sf) +
  geom_sf(fill = "lightgrey", data = gis_sf) +
  geom_sf(aes(fill = cluster), color = NA) +
  geom_sf(color = alpha("black", 1), fill = NA, data = gis_sf) +
  scale_fill_viridis_d(option = "plasma", direction = 1, name = "Cluster") +
  labs(title = paste0("Clustered solar sites by region",
                      ", sd_loss <= ", params$sol_cl_tol * 100, "%")) +
  rev_theme_map()
ggsave_map(glue("locid_sol_cl_sf_{sol_cl_mask}.png"), path = p$dir$fig_mod,
           scale = 1.25)



# #=========================================#
# 
# locid_sol_cl_sf <- locid_sol_cl %>%
#   left_join(
#     select(locid_sol_sf, 
#            any_of(c("reg_off", "region", "locid", "cluster", "offshore")),
#            starts_with("saf_"))
#   ) %>%
#   filter(!is.na(cluster), sol_MW_max > 0) %>%
#   mutate(cluster = factor(cluster)) %>%
#   st_as_sf()
# 
# ggplot(locid_sol_cl_sf) +
#   geom_sf(fill = "lightgrey", data = gis_sf) +
#   geom_sf(aes(fill = as.numeric(cluster)), 
#           color = NA,
#           # color = alpha("white", .5)
#           ) +
#   geom_sf(color = alpha("black", 1), fill = NA, data = gis_sf) +
#   # scale_fill_viridis_c(option = "H", direction = 1, name = "Cluster") +
#   scale_fill_distiller(palette = "RdYlBu", direction = 1, name = "Cluster",
#                        limits = range(1, p$sol_cl_max, 100)) +
#   labs(title = paste0("Clustered solar sites by region")) +
#   rev_theme_map()
# ggsave("locid_sol_cl_sf.png", path = p$dir$fig_mod, 
#        height = 5, width = 6, scale = 1.2)
# 
# ggplot(locid_sol_cl_sf) +
#   # geom_sf(fill = "lightgrey", data = gis$mod_map$sf) +
#   geom_sf(aes(fill = saf_tl), color = alpha("white", .5)) +
#   geom_sf(color = alpha("black", 1), fill = NA, data = gis_sf) +
#   scale_fill_viridis_c(option = "magma", direction = 1) +
#   labs(title = paste0("Clustered within regions solar sites")) +
#   rev_theme_map()
# ggsave("locid_sol_cl_sf-saf_tl.png", 
#        path = p$dir$fig_mod, height = 5, width = 6, scale = 1.5)
# 
# fname <- file.path(p$dir$data_mod, glue("locid_sol_{sol_cl_mask}_sf.RData"))
# message("Saving: ", fname)
# save(locid_sol_cl_sf, file = fname); rm(fname)

```


### Aggregate

Aggregated capacity factors by region and cluster. 

```{r}
merra_sol_cl <- merra_solar %>%
  filter(locid %in% unique(locid_sol_cl_sf$locid)) %>% # drop unused locations
  mutate(slice = timeslices::dtm2tsl(UTC)) %>% # create time-slice IDs
  select(locid, slice, starts_with("scf")) %>% # drop unused columns
  left_join( # merge with gis-data
    select(st_drop_geometry(locid_sol_cl_sf), 
           locid, region, reg_off, offshore, cluster, sol_MW_max), 
    relationship = "many-to-many"
  ) %>%
  group_by(slice, reg_off, cluster) %>%
  summarise(
    scf_fh = round(weighted.mean(scf_fh, sol_MW_max, na.rm = T), 3),
    scf_fl = round(weighted.mean(scf_fl, sol_MW_max, na.rm = T), 3),
    scf_tl = round(weighted.mean(scf_tl, sol_MW_max, na.rm = T), 3),
    scf_td = round(weighted.mean(scf_td, sol_MW_max, na.rm = T), 3),
    # geometry = st_union(geometry),
    .groups = "drop"
  ) %>%
  mutate(year = params$wyear, .before = 1) %>%
  as.data.table()
merra_sol_cl
summary(merra_solar$scf_fl)
summary(merra_solar$scf_tl)
summary(merra_solar$scf_td)

fname <- 
  file.path("tmp", glue("merra_sol_{sol_cl_mask}_{wyear}.fst"))
write_fst(merra_sol_cl, fname, 100); rm(fname)

sol_GW_max_sf <- locid_sol_cl_sf %>% 
  # st_drop_geometry() %>% 
  # select(region, offshore, sol_MW_max) %>% 
  filter(sol_MW_max > 0) %>%
  st_make_valid() %>%
  group_by(region, reg_off, offshore, cluster) %>% 
  reframe(
    scf_fh = weighted.mean(saf_fh, sol_MW_max, na.rm = T),
    scf_fl = weighted.mean(saf_fl, sol_MW_max, na.rm = T),
    scf_tl = weighted.mean(saf_tl, sol_MW_max, na.rm = T),
    scf_td = weighted.mean(saf_td, sol_MW_max, na.rm = T),
    # area = sum(area, na.rm = T), 
    sol_GW_max = sum(sol_MW_max, na.rm = T) / 1e3, 
    geometry = rev_union_polygons(geometry)) %>%
  st_as_sf() %>% st_make_valid()

ggplot() +
  geom_sf(color = alpha("black", .25), fill = "lightgrey", data = gis_sf) +
  geom_sf(aes(fill = scf_tl), data = sol_GW_max_sf) +
  # geom_sf(data = locid_grid_sf, fill = NA, color = "white") +
  scale_fill_viridis_c(option = "H", direction = 1) +
  # labs(title = paste0(p$country, ", wind locations with cf >= ", 
                      # params$win_gwa_cf_min, " (GWA)")) +
  rev_theme_map()
ggsave(glue("locid_sol_cl_sf-{sol_cl_mask}_{wyear}.png"), 
       path = "tmp", height = 5, width = 6, scale = 1)

save(sol_GW_max_sf, file = file.path("tmp", "sol_GW_max.RData"))

```















## Select region
```{r, eval=FALSE}
r <- which(gis_sf0$reg32 == "KA"); r
gis_sf0[r,]
# plot(gis_sp[r,], add = F)

gis_sf <- st_transform(gis_sf0[r,], crs = st_crs(obj0_tr))
plot(gis_sf[1], axes = T)
gis_sv <- vect(gis_sf)
plot(gis_sv)

obj_tr <- crop(obj0_tr, gis_sv) # optional, crop the map
plot(obj_tr)
obj_tr
obj_tr <- mask(obj_tr, gis_sv) # optional, select land only
plot(obj_tr)
summary(obj_tr)
num <- as.numeric(obj_tr)
hist(num)

# keep locations with high potential (>= 20% annual load)
obj_tr_hp <- app(obj_tr, fun = function(x) {x[x < .30] <- NA; return(x)})
plot(obj_tr_hp, main = "Locations with >= 30% load")

# coerce raster data to vector-map
v3 <- as.polygons(obj_tr_hp)
plot(v3, col = "dodgerblue", main = "Areas with >= 30% load")

if (!any(is.valid(v3))) { # fix errors
  v3 <- makeValid(v3)
  # is.valid(o)
}

area_thresh <- units::set_units(100, "km^2")
v4 <- smoothr::drop_crumbs(v3, area_thresh)
plot(v4, add = F, border = "navy", col = "grey")

buffer_km <- units::set_units(1000, "m")
v5 <- terra::buffer(v4, buffer_km)
plot(v5, add = F, border = "navy", col = "grey")

simpl_km <- units::set_units(.001, "km")
v6 <- terra::simplifyGeom(v5, simpl_km)
plot(v6, add = F, border = "navy", col = "grey")

# coerce to sf-format
sim_sf <- sf::st_as_sf(v6) %>% st_union()
sim_sf <- st_set_crs(sim_sf, st_crs(gis_sf))

# plot(sim_sf$geometry[1], col = "dodgerblue", border = "navy")
# plot(sim_sf$geometry[2], col = "red", border = "red", add = T)


# simplify
# buf_sf <- st_buffer(s3, dist = .0, )
# plot(buf_sf$geometry, col = "dodgerblue", border = "navy")
# sim_sf <- st_simplify(s3, dTolerance = 1)
# size(sim_sf)
plot(sim_sf, col = "dodgerblue", border = "navy", axes = T,
     main = "Areas for potential developement of wind power plants")
# save for further use
wind_select_sf <- sim_sf %>% st_as_sf()
dir.create("tmp/data/NREL", recursive = T, showWarnings = F)
save(wind_select_sf, file = paste0("tmp/data/NREL/wind_select_", r,"_ge30_sf.RData"))

```

```{r}
library(nrel.dev.api)

q_atributes <- paste0("windspeed_", 
                      c(40, 80, 100, 120), 
                      "m", collapse = ",")
collection <- "india-wind"
q_api_url <- get_nrel_url(collection)
q_interval = 15

?guess_nrel_grid
grid_KA <- guess_nrel_grid(wind_select_sf,
                           dx = .02, dy = .02, 
                           collection = collection,
                           q_atributes = q_atributes, 
                           q_interval = q_interval)

ggplot() +
  geom_sf(data = gis_sf, fill = "wheat") +
  geom_sf(data = grid_KA$grid_sf, fill = NA, color = "blue", shape = ".") +
  # geom_sf(data = gis_rot_geom, fill = NA, color = "blue") +
  # geom_sf(data = gpts, color = "red", shape = ".") +
  theme_bw()

?fetch_data_from_grid
nrel_data <- fetch_data_from_grid(grid_KA$grid_sf,
                     limit = 3,
                     save_by = 2,
                     save_dir = "tmp/KA",
                     file_prefix = "test",
                     collection = collection,
                     atributes = q_atributes,
                     names = "2014",
                     interval = q_interval, 
                     )

nrel_data <- fetch_data_from_grid(nrel_data$grid_sf,
                     limit = 3,
                     save_by = 2,
                     save_dir = "tmp/KA",
                     file_prefix = "test",
                     collection = collection,
                     atributes = q_atributes,
                     names = "2014",
                     interval = q_interval, 
                     )


```

## read data
```{r}
library(nrel.dev.api)
library(future.apply)
library(sf)
# ff <- list.files("F:/NREL/IND", pattern = "IND_WB.+RData", full.names = T); ff
# reg <- "GJN"
# reg <- "KLY"
# reg <- "TNY"
# reg <- "APY"
# reg <- "KLY"
# reg <- "MP"
# reg <- "RJ"
# reg <- "OR"
# reg <- "TNY.off"
# reg <- "GJN.off"
# reg <- "WB.off"
# reg <- "MH.off"
# reg <- "APY.off"
# reg <- "TNY.off"
# reg <- "OR.off"

ff <- list.files(
  # "F:/NREL/IND",
  "C:/Users/olugo/Documents/R/globalwindatlas/tmp/NREL/IND",
  pattern = paste0("IND_", reg,".+RData"), full.names = T); basename(ff)
plan(multisession, workers = 7)
f <- ff[1]; f
try(rm(x)); gc()
x <- lapply(ff, FUN = function(f) {
  cat(basename(f), "\n")
  o <- load(f)
  # o <- load(ff[1])
  # r <- get(o)[["raw"]][[1]]
  # mm <- future_lapply(get(o)[["raw"]], function(r) {
  mm <- future_lapply(get(o)[["raw"]], function(r) {
    # browser()
    if (is.null(r) || is.null(r$status_code) || r$status_code != 200) return(NULL)
    ll <- nrel_read_responce(r)
    # browser()
    m <- ll$meta
    ll <- ll$data
    ii <- sapply(ll, function(x) class(x) == "numeric")
    for (n in names(ll)[ii]) {
      # cat(n, format(lubridate::now()), "\n")
      ll[[n]] <- as.integer(100 * ll[[n]])
    }
    # m <- ll$meta
    # ll <- ll$data
    # browser()
    ll[, lon := m$Longitude]
    ll[, lat := m$Latitude]
    return(ll)
  })
  mm <- rbindlist(mm)
  return(mm)
})
plan(sequential)
x %>% length()
# str(x)
# sapply(x[[1]], class)
x <- rbindlist(x)
gc()
dim(x)
x <- unique(x)
dim(x)
gc()
write_fst(x, 
          paste0(
            # "D:/Dropbox/India/IDEEA/ideea_data/nrel/IND_", 
            "D:/Dropbox/India/IDEEA/ideea_data/nrel/IND_", 
            reg, "_wind_5m.fst"),
          compress = 100)
# write_fst(x, "tmp/NREL/IND_KA_data.fst", compress = 100)
# write_fst(x, "tmp/NREL/IND_WB_data.fst", compress = 100)
# write_fst(x, "F:/NREL/IND/IND_WB_data.fst", compress = 100)
# rm(dat)
# gc()
# installr::os.sleep(first_turn_hibernate_off = F)

# dat <- read_fst("F:/NREL/IND/IND_KA_data.fst")
# 
# class(dat$Year)
# ii <- sapply(dat[1,], function(x) class(x) == "numeric")
# 
# x <- dat[1:5,]
# sapply(x, class)
# 
# for (n in names(dat[1,])[ii]) {
#   cat(n, format(lubridate::now()), "\n")
#   dat[[n]] <- as.integer(100 * dat[[n]])
# }
# sapply(dat, class)
# gc()
# write_fst(dat, "F:/NREL/IND/IND_KA_data.fst", compress = 100)
# head(dat)

```



